A Gaussian process model of human electrocorticographic data

### 2020-02-17 paper/main.tex
working on results section-- updated network results

>>>>

To gain additional insight into which regions were most informative about
full-brain activity patterns at different frequency ranges, we next computed (for each frequency range)
the intersection of the top 10\% highest information scores across the maps for
Datasets 1 and 2 (analogous to our approach in Fig.~\ref{fig:informap}C).
This yielded a single map of the (reliably) most informative locations for each frequency range we examined.
We then carried out two \textit{post hoc} analyses on each of these maps to better characterize
the underlying structural and functional properties of each set of regions we identified
as being particularly informative about one or more neural patterns.

A growing body of neuroscientific research is concerned with characterizing the \textit{parcellations}
of anatomical and functional brain networks~\citep[for review see][]{ZaleEtal10, ArslEtal18}.
The dominant approaches entail obtaining a full-brain connectivity matrix using either diffusion tensor imaging to identify the brain's network of
white matter connections, or functional connectivity (typically applied to resting state data) to
correlate the patterns of activity exhibited by different brain structures.  One can then apply graph theoretic approaches
to assign each brain structure (typically a single fMRI voxel) to one or more networks~\citep[for review see][]{BullSpor09}.
The result is a set of distinct (or partially overlapping) brain ``networks'' that may be
further examined to elucidate their potential functional role.  We overlaid a well-cited seven-network
parcellation map identified by \cite{YeoEtal11} onto the maps of brain locations that were most informative
about each neural pattern.  For each of these information maps, we computed the proportion of voxels in the most informative
brain regions that belonged to each of the seven networks identified by \cite{YeoEtal11}.
We found that the regions we identified as being most informative about different neural patterns varied
markedly with respect to which functional networks they belonged to (Fig.~\ref{fig:networks}A, B).  This is consistent with
the notion that there is no ``universal'' brain region that consistently reflects activity in the rest of the brain.  Rather,
each region's activity patterns appear to be characterized by different spectral profiles, and the ability to
infer activity patterns at a particular frequency range depends on the structural and functional
connectome specific to that frequency range.

%next: neurosynth
